Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-01-03 Paper.tex
renamed gasUsed abbreviation in Block header
clearer definition of transaction

A transaction (formally, $T$) is a single cryptographically-signed instruction sent by an actor external to Ethereum. An external actor can be a person (via a mobile device or desktop computer) or could be from a piece of automated software running on a server. There are two types of transactions: those which result in message calls and those which result in the creation of new accounts with associated code (known informally as `contract creation'). Both types specify a number of common fields:

>>>>

A transaction (formally, $T$) is a single cryptographically-signed instruction sent by a node in the Ethereum network. There are two types of transactions: those which result in message calls and those which result in the creation of new accounts with associated code (known informally as `contract creation'). Both types specify a number of common fields:
